Testing Rate of Change Transition models

### 2023-05-23 minos/testing/rate_of_change_testing.Rmd
Added violin plots to the utils script (and removed na values in the quantile func so we can plot raw data also), and added them to the rate_of_change_testing notebook

>>>>

### hh_income

```{r}
income.spag.base <- spaghetti_plot(base.dat, 'hh_income')
income.spag.base
```

This one actually looks worse I think... Might need to have a look at subsetting to see the tight band in the middle in more detail. Also worth using the same plot on raw data to see how that looks:

```{r}
income.spag.raw <- spaghetti_plot(raw.dat, 'hh_income')
income.spag.raw
```

Very useful plot! Much more variability in the raw data that we don't keep hold of in the simulation. Also shows that the spike in 2015 is mostly due to about 5-6 data points by the looks of things. Again worth a chat with the group to figure out where our acceptable thresholds are, as we are unlikely to be able to capture all of the heterogeneity in such a varied and skewed variable like hh_income.

### SF_12_MCS

Quick look at SF_12_MCS also.

```{r}
sf12.spag.base <- spaghetti_plot(base.dat, 'SF_12')
sf12.spag.base

sf12.spag.raw <- spaghetti_plot(raw.dat, 'SF_12')
sf12.spag.raw
```
Need to remove missing values.

## Violin Plots

### hh_income

```{r}
income.violin.base <- violin_plot(base.dat, 'hh_income')
income.violin.base

income.violin.raw <- violin_plot(raw.dat, 'hh_income')
income.violin.raw
```

### SF12

```{r}
sf12.violin.base <- violin_plot(base.dat, 'SF_12')
sf12.violin.base

sf12.violin.raw <- violin_plot(raw.dat, 'SF_12')
sf12.violin.raw
```
